---
title: "Schedule"
format: html
---

::: callout-note
-   Our venue has changed! We will now be hosting in-person participants at 275 George Street, Brisbane. 
-   The agenda and timing may change. Watch this space for developments 👀
-   All listed times are in Australian Eastern Standard (Brisbane) time.
-   Make sure you have [registered](https://forms.gle/8p8aXELgcbedA9up8){target="_blank"} to access links for online meeting spaces.
-   We are working hard to ensure all activities are accessible for both online and in person attendees.
:::

```{=html}
<style>
.event-card {
  padding: 10px;
  margin-bottom: 10px;
  border-radius: 6px;
  border-left: 6px solid rgba(0,0,0,0.2);
}

/* Colour by type */
.talk { background: #9DC1DA; } 
.workshop { background: #A7D9DF; }
.social { background: #C8BCDA; }
.general { background: #DAD6E2; }

.event-time {
  font-size: 0.8em;
  color: #555;
}

.event-title {
  font-weight: 600;
  margin-bottom: 4px;
}

/* description styling */
.event-desc {
  font-size: 0.85em;
  color: #555;
  margin-top: 4px;
  line-height: 1.4;
}
</style>
```
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(htmltools)
library(yaml)

schedule <- yaml::read_yaml("schedule.yml")

# Convert YAML description into HTML
format_desc <- function(desc) {
  if (is.null(desc)) return(NULL)

  # Convert bullet list
  lines <- unlist(strsplit(desc, "\n"))

  tags$div(
    class = "event-desc",
    lapply(lines, function(line) {
      line <- trimws(line)

      if (startsWith(line, "- ")) {
        tags$div(paste0("• ", substring(line, 3)))
      } else {
        # tags$div(line)
        tags$div(HTML(line))   # ✅ THIS is the critical fix
      }
    })
  )
}

render_day <- function(day) {
  events <- schedule[[day]]

  div(
    lapply(events, function(e) {

      div(
        class = paste("event-card", e$type),

        div(class = "event-time",
            paste(e$start, "-", e$end)),

        div(class = "event-title", e$name),

        format_desc(e$description)
      )
    })
  )
}
```

```{=html}
<div style="display:flex; gap:20px; margin-bottom:15px; flex-wrap:wrap;">

  <div style="display:flex; align-items:center; gap:6px;">
    <div style="width:15px; height:15px; background:#DAD6E2;"></div>
    <span>General</span>
  </div>

  <div style="display:flex; align-items:center; gap:6px;">
    <div style="width:15px; height:15px; background:#9DC1DA;"></div>
    <span>Talk</span>
  </div>

  <div style="display:flex; align-items:center; gap:6px;">
    <div style="width:15px; height:15px; background:#A7D9DF;"></div>
    <span>Workshop</span>
  </div>

  <div style="display:flex; align-items:center; gap:6px;">
    <div style="width:15px; height:15px; background:#C8BCDA;"></div>
    <span>Food/Social</span>
  </div>

</div>
```
::: panel-tabset
### Monday 10 Aug

```{r, echo=FALSE, warning=FALSE, message=FALSE}
render_day("Monday")
```

### Tuesday 11 Aug

```{r, echo=FALSE, warning=FALSE, message=FALSE}
render_day("Tuesday")
```

### Wednesday 12 Aug

```{r, echo=FALSE, warning=FALSE, message=FALSE}
render_day("Wednesday")
```

### Thursday 13 Aug

```{r, echo=FALSE, warning=FALSE, message=FALSE}
render_day("Thursday")
```

### Friday 14 Aug

```{r, echo=FALSE, warning=FALSE, message=FALSE}
render_day("Friday")
```
:::

## Lightning round {#lightning}

Prepare a short introduction (\~2 minutes):

-   your name\
-   your organisation\
-   one current challenge\
-   one thing you hope to learn

## Poster session {#poster}

As a jurisdiction, bring a digital poster representing your work, team, or context. This is intentionally flexible! Ideas include:

-   a flagship stock assessment\
-   a challenging case study\
-   your team and region ("getting to know us")\
-   a methodological innovation\
-   a collaboration success story
